Improving the portuguese hyphenation rules

### 2023-04-13 article/article.tex
adding widespread of TeX hyphenations

@@

>>>>

Despite the fact that \TeX{} hyphenation algorithm and rules are old, they are,
to these days, the most frequently used even outside the \TeX{}'s world. For
example, Hunspell is a spell checker and morphological analyzer that is adopted
in may software (e.g. LibreOffice, OpenOffice.org, Mozilla Firefox, Mozilla
Thunderbird, Google Chrome, macOS, InDesign, memoQ, Opera, Affinity Publisher,
among others \cite{hunspell}). Hunspell uses \TeX{} hyphenation rules
\cite{hunspellhyphen}, making \TeX{} hyphenation widespread in the computer
world. That is a result of \TeX{} approach simplicity and versatility. The
algorithm works well, it is currently used in 66 languages
\cite{texhyphenrules} and it is possible to design new rules for those missing
languages.

@@

\section{Creating the dictionary}
A \emph{bash} script was created to crawl on six online dictionaries and extract a word hyphenation, when found.

\section{Old Text}
